---
title: "DDP: Slide and Plotly Project"
author: "Kurtis Pivert"
date: "5/14/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}

        ## Load Required Packages

        require(plotly)
        require(knitr)
        require(tidyverse)
        require(extrafont)
        loadfonts(quiet = TRUE)        

```

## DDP: Slide and Plotly Project

### **Kurtis Pivert -- May 14, 2017**
#### *Project Motivation*

For this week's project, we're required to 

- Create a web page presentation using R Markdown 
- The web page must contain the date the document was created 
- The presentation must feature a plot created with Plotly
- Host the web page on either GitHub Pages, RPubs, or NeoCities

## Plotly Visualizations

For this project, I've created three very basic plots that demonstrate the power of
the `Plotly` package. 

These include:

- Histogram
- Line chart created in `ggplot` and converted to Plotly
- 3D Scatterplot

## Histogram
One line of code creates a basic histogram. 

```{r Histogram, echo=TRUE}
        plot_ly(mtcars, x = ~wt, type = "histogram")
```

## Line Chart with GGPlot Converted to Plotly Interactive

```{r GGPLOT, echo=FALSE, cache= TRUE, message=FALSE, warning=FALSE}
        
         g <- ggplot(economics_long, aes(x=date, y= log(value), color = variable))+
                geom_line()+
                theme_bw(base_family = "Roboto")+
                ylab(label = "Log Values")+
                xlab(label = "Date")+
                ggtitle(label = "US Economic Variables Over Time (Log Values)")+
                theme(plot.title = element_text(hjust = 0.5))
                
         ggplotly(g)

```


## 3D Scatterplot Using the `iris` Dataset

```{r 3D Scatterplot, echo = TRUE}
        
        plot_ly(iris, x = ~Sepal.Length, y = ~Sepal.Width, z = ~Petal.Length, 
                color = ~Species, type = "scatter3d", mode= "markers")
```

## Thanks for Your Review

I'd welcome your feedback and suggestions for improvement. Please email me at 
[kurtis.pivert@gmail.com](mailto:kurtis.pivert@gmail.com).





